Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-19 tex/sections/consensus.tex
Fix an error
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The committee of delegates is responsible for creating new blocks of the Argennon blockchain, and it issues a
certificate for every block of the Argennon blockchain. A certificate needs to be signed
by \textbf{all} of the committee members in order to be considered valid.

@@

A block certified only by the delegates committee is credible, but is not considered completely final until it
receives the certificate of its validator assembly. Since a block at height $h$ contains the validators certificate
of the block at height $h-k$, the unvalidated part of the blockchain can not be longer than $k$ blocks.

The committee of delegates may use any type of agreement protocol to reach consensus on the
next block. Usually, the delegates are large organizations, and they can communicate with each
other efficiently using their reliable networking infrastructure. This mostly eliminates the complications of their
consensus protocol and any protocol will have a good performance in practice. Usually a very simple and fast protocol
can do the job: one of the members is randomly chosen as the proposer, and other members vote "yes" or "no" on the
proposed block. For better performance, they should run their agreement protocol for reaching consensus about small
batches of transactions in their mem-pools, instead of the whole next block.

If one of the delegates loses its network connectivity, no new blocks can be generated. For this reason,
the delegates should invest on different types of communication infrastructure, to make sure they never lose
connectivity to each other and to the Argennon network.

@@

Every \texttt{AssemblyLifeTime} number of blocks, randomly $m$ assemblies are selected from
validators, in a way that the total stakes of assemblies are almost equal, and every
account is a member of \textbf{at least} one assembly.\footnote{An account can be the member of multiple assemblies.}

The value of $m$ is determined by the ADAGs, but it can never be higher than $32$. This way, it is guaranteed
that on average, any block of the Argennon blockchain is validated by at least $3\%$ of the total ARG supply.

@@

Every validator has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is part of the staking database. A validator can change
his status to \texttt{offline} through an external request (transaction) to the ARG application. In this request he
exactly specifies for how long he wants to be offline and after this period his status will automatically be considered
\texttt{online} again. When a validator sets his status to \texttt{offline} for some period of time, he
will receive a small portion of the maximum possible reward that a validator can receive in that period of time by
actively participating in the consensus protocol. This ensures that a validator has an incentive for changing his
status to offline rather than simply becoming inactive.

The staking database of a validator assembly can only be updated by the assembly itself. That means, an external
request which changes the status of a validator can only be included in a block that is being validated by the
assembly of that validator.

@@

A block certificate issued by some members of a validators assembly is considered valid, if according to
the staking database of the previous block \textbf{certified by the same assembly}, we have:\footnote{If we calculate
the stake values based on the previous block, a malicious assembly can select the validators of the next block.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the assembly is higher than \texttt{minOnlineStake} fraction
    of the total stake of the assembly. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the assembly members that have \texttt{online} status.
\end{itemize}

@@

\subsubsection{Certificate Signing}

The delegates can generate blocks very fast. Therefore, the Argennon blockchain always has an
unvalidated part which contains the blocks that have a certificate from the committee of delegates but have not
yet received a certificate from the validators.

As we mentioned before, the block with height $h$ needs a certificate from the assembly of
validators with index $h$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity of the block (See Section~\ref{subsec:block-validation}), and if the block is valid, he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validator assembly of the previous block.
Some validators may also require seeing a certificate from
some community based committees. An honest validator never signs a certificate for two different blocks with the
same height.

@@

We analyze the minimum amount of stake that is required for conducting different types of attacks against the Argennon
blockchain. In these attack scenarios, we assume that a single validator assembly is corrupted, all the delegates
are malicious and the adversary is able to partition the network arbitrarily.

We denote the total stake of the corrupted validator assembly with $s$ and the total stake of malicious users of the
assembly with $m$. We use $d$ to denote the stake of the assembly's users with \texttt{offline} status and $h$ to denote
the total stake of the assembly's users with \texttt{online} status that do not participate in the
protocol.\footnote{$d$ stands for \emph{deactivated} and $h$ stands for \emph{hidden}.} We assume
that a certificate is accepted if it is signed by more than $r$ fraction of the total online stake of the assembly.
We obtain the minimum required malicious stake for three types of attacks:
\begin{itemize}
    \item Confirming an invalid block:
    \[ m > r(s-d) \]
    \item Forking the blockchain by double voting and network partitioning:
    \[m > (2r-1)(s-d)+h \]
    \item Halting the blockchain by refusing to vote:
    \[m > (1-r)(s-d)-h \]
\end{itemize}

In Argennon we have $r=\frac{3}{4}$ and $d < \frac{1}{3}s$.
Consequently, in Argennon to confirm an invalid block, the adversary needs at least $\frac{1}{2}$ of the total stake
of the assembly. For forking the blockchain, interestingly $m$ is
minimized when $h=0$, and $\frac{1}{3}s$ is the minimum required stake. For halting the blockchain,
an adversary requires a stake higher than $\frac{1}{6}s-h$.

@@

To compare the minimum stake required for halting the blockchain in two protocols, we can solve the following
inequality:
\[
    \frac{1}{4}(s-d)-h > \frac{1}{3}s-h\ \cdot
\]
We observe that as long as $d>\frac{1}{9}s$, the minimum required stake for halting the blockchain is higher in the
Argennon protocol.

>>>>

The committee of delegates is responsible for creating new blocks of the Argennon blockchain, and issues a
certificate for every block of the Argennon blockchain. The certificate needs to be signed
by \textbf{all} the committee members in order to be considered valid.

@@

A block certified only by the committee of delegates is relatively credible, but it is not considered final
until its next block receives the certificate of its validator assembly. Since a block at height $h$ contains the
validators certificate of the block at height $h-k$, the unvalidated part of the Argennon blockchain can not be longer
than $k$ blocks.

The committee of delegates may use any type of agreement protocol to reach consensus on the
next block. Usually the delegates are large organizations, and they can communicate with each
other efficiently using their reliable networking infrastructure. This mostly eliminates the complications of their
consensus protocol and any protocol could have a good performance in practice. Usually a very simple and fast protocol
can do the job: one of the members is randomly chosen as the proposer, and other members vote ``yes'' or ``no'' on the
proposed block. For better performance, the delegates should run their agreement protocol for reaching consensus about
small batches of transactions in their mem-pools, instead of the whole next block.

If one of the delegates loses its network connectivity, no new blocks can be generated. For this reason,
the delegates should invest on different types of communication infrastructure, to make sure they will never lose
connectivity to each other and to the Argennon network.

@@

Every \texttt{AssemblyLifeTime} number of blocks, randomly $m$ assemblies are selected from
validators, in a way that the total stakes of different assemblies are almost equal, and every
account is a member of \textbf{at least} one assembly.\footnote{An account can be a member of multiple assemblies.}

The value of $m$ is determined by the ADAGs, but it can never be higher than $32$. This way, it is guaranteed
that on average, any block of the Argennon blockchain is validated by at least $2\%$ of the total ARG supply.

@@

Every validator has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is part of the staking database. A validator can change
his status to \texttt{offline} through an external request (transaction) to the ARG application. In this request he
exactly specifies for how long he wants to be offline and after this period his status will be automatically considered
\texttt{online} again. When a validator sets his status to \texttt{offline} for some period of time, he
will receive a small portion of the maximum possible reward that a validator can receive in that period of time by
actively participating in the consensus protocol. This ensures that a validator has an incentive for changing his
status to offline rather than simply becoming inactive.

The staking database of a validator assembly can be updated only by the assembly itself. That means, an external
request which changes the status of a validator can be included only in a block that is validated by the assembly of
that validator.

@@

A block certificate issued by some members of a validators assembly is considered valid, if according to
the staking database of the previous block \textbf{certified by the same assembly}, we have:\footnote{If we calculate
the stake values based on the previous block, a malicious assembly can select the validators of the next block by
manipulating the staking database.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the assembly is higher than \texttt{minOnlineStake} fraction
    of the total stake of the assembly. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the assembly members that have \texttt{online} status.
\end{itemize}

@@

The merging will continue recursively until the online stake of all remaining assemblies is higher than
\texttt{minOnlineStake}. If eventually all assemblies get merged together and only one assembly remains, the condition
for validity of block certificates changes: A certificate of validators will be considered valid if the sum of stakes
of the certificate signers is higher than $2/3$ of the total stake of validators and \texttt{online/offline}
status of validators becomes ineffective.

\subsubsection{Signing the Block Certificate}

The delegates can generate blocks very fast. Consequently, the Argennon blockchain always has an
unvalidated part which contains the blocks that have a certificate from the committee of delegates but have not
yet received a certificate from the validators.

As we mentioned before, the block with height $h$ needs a certificate from the assembly of
validators with index $h$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity of the block (See Section~\ref{subsec:block-validation}), and if the block is valid, he issues
an ``accept'' signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validator assembly of the previous block.
Some validators may also require seeing a certificate from
some community based committees. An honest validator never signs a certificate for two different blocks with the
same height.

@@

We analyze the minimum amount of stake that is required for conducting different types of attacks against the Argennon
blockchain. In these attack scenarios, we assume that a single validator assembly is corrupted, all the delegates
are malicious and the adversary is able to fully control message transmission and partition the network arbitrarily.

We denote the total stake of the corrupted validator assembly with $s$ and the total stake of malicious users of the
assembly with $m$. We use $d$ to denote the stake of users of the assembly who have \texttt{offline} status and $h$
to denote the stake of users of the assembly who have \texttt{online} status and do not participate in the
protocol.\footnote{$d$ stands for \emph{deactivated} and $h$ stands for \emph{hidden}.} We assume
that a certificate is accepted if it is signed by more than $r$ fraction of the total online stake of the assembly.
We obtain the minimum required malicious stake for three types of attacks:
\begin{itemize}
    \item Confirming an invalid block:
    \[ m > r(s-d) \]
    \item Forking the blockchain by double voting and network partitioning:
    \[m > (2r-1)(s-d)+h \]
    \item Halting the blockchain by refusing to vote:
    \[m > (1-r)(s-d)-h \]
\end{itemize}

In Argennon we have $r=\frac{3}{4}$ and $d < \frac{1}{3}s$.
Consequently, in Argennon to confirm an invalid block, the adversary needs at least $\frac{1}{2}$ of the total stake
of an assembly. For forking the blockchain, interestingly $m$ is
minimized when $h=0$, and $\frac{1}{3}s$ is the minimum required stake. For halting the blockchain,
an adversary requires a stake higher than $\frac{1}{6}s-h$.

@@

To compare the minimum stake required for halting the blockchain in two protocols, we can solve the following
inequality:
\[
    \frac{1}{4}(s-d)-h > \frac{1}{3}s-(d+h)\ \cdot
\]
We observe that as long as $d>\frac{1}{9}s$, the minimum required stake for halting the blockchain is higher in the
Argennon protocol and the value of $h$ does not matter.
